\documentclass[12pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{datatool}
\author{Nathaniel Beaver}
\title{A Table of Commutation Relations}

\usepackage[numbers]{natbib}
\usepackage[pdftex,bookmarks=true]{hyperref}
\hypersetup{
    pdftitle={A Table of Commutation Relations},
    pdfauthor={Nathaniel Beaver}
}

\usepackage{braket} %Bra ket notation

\begin{document}
\maketitle

\section{A table of commutation relations for operators of a single particle.}

\subsection{Operators to use.}

\begin{itemize}
\item Observables (Hermitian): $x, p_x, H=\frac{p_x^2}{2m}, N=a^\dagger a, J_x, J_y, J_z, J, \hyperref[def_Pi]{\Pi}$
\item Non-observables: $a, a^\dagger, T, $
\end{itemize}

\subsection{The table.}
\begin{align}
[B, B] &= 0\\
[p_x, x] &= - i\hbar \label{canbasic}\\
[p_x, V(x)] &= -i\hbar \frac{\partial}{\partial_x} V(x)\\
[N, a] &= - a\\
[a, a^\dag] &= 1\\
\end{align}
\subsubsection{Canonical commutation relations}
Relation \ref{canbasic} is an example of a canonical commutation relation. In general if $q_i$ are coordinates and $\pi_i$ are the canonically conjugate momenta to $q_i$, then
\begin{equation}
[\pi_i, q_j] = -i\hbar \delta_{ij}
\end{equation}

\subsubsection{Spin}
In general,
\begin{align}
  [S_i, S_j] &= i\hbar \varepsilon_{ijk} S_k\\
  [S_i, \mathbf{S}^2] &= 0
\end{align}
In addition, for spin-1/2 particles
\begin{align}
\{S_a, S_b\} = \hbar^2/2 \delta_{ab} . 
\end{align}

%\begin{tabular}{ l | r r }
%            & $x$ & $p_x$ \\
%\hline
%  $x$ & \hyperref[self]{$0$} & \hyperref[unc]{$i \hbar$}\\
%  \hyperref[def_p_x]{$p_x$} & $-i\hbar$ & $0$ \\
%\end{tabular}



\subsection{Operator definitions.}
\begin{itemize}
\item \label{def_p_x} $p_x = \frac{\hbar}{i}\frac{\partial}{\partial x}$ in the x-basis. Townsend p.158.
\item \label{def_Pi} $\Pi\ket{x}=\ket{-x}$ Townsend p.213.
\item \label{def_H} $H = \frac{p^2}{2m} + V(x)$ Sakurai p.97, (2.4.2). 
\end{itemize}

\subsection{References.}
\begin{itemize}
\item[0] \label{self} Any operator commutes with itself.
\item[$-i \hbar$] \label{unc} See Townsend eq. 6.31, p. 155 or Griffiths eq. 2.51, p.55. This leads to the uncertainty principle $\Delta x \Delta p_x \geq \frac{\hbar}{2}$.
\item[$-a$] \label{N-a} See Sakurai p.90, (2.3.10).
\item[$-a^\dagger$] \label{N-aDag} See Sakurai p.90, (2.3.11).
\item[0] \label{H-p_x} By the product rule.
\end{itemize}

\section{A table of commutation relations for operators of two particles.}

\end{document}
